
%==============================================================
%
%	File Nam:	 	George Dane
%	Date:			09/09/2021
%
%	Author:			Adam Kalinowski
%	Version:		v..
%	Liscense:
%
%	Purpose:
%	Details:
%
%==============================================================

\documentclass[10pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{fourier}
\usepackage[mathscr]{eucal}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{thmtools}
\usepackage{mdframed}
\usepackage{wasysym}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Adam Kalinowski}
\title{Anthology of the Occult}
\begin{document}
\maketitle
\part{The possesion of Jeremey Loch}
\chapter{}
\par ``I just dont know what to do.''\\
``Yes I know my child.'' The father cleared his throat and continued, ``In these types of cases, we need to pass through red tape as thick as the earth itself. You have to understand--''\\
``Understand what exactly?'' I spoke up. i pulled my hands out of my jeans, ``What the hell are we doing here? We are supposed to be helping their son and you want to talk about red tape.''\\
``Father Peter, I can assure you--''\\
``I am not a father.'' I said it plainly, and I had a mind to continue my grievences, but the mother spoke up:\\
``Then what are you? Why are you here? You haven't done anything since you have gotten here. All you have done is smoke and drink\ldots CONSTANTLY.'' She shook her head violently, ``You are drunk right now I bet. and you have the audacity to even discount my religion. Father O'Hennessy--''\\
``Has done absolutely nothing! But here is the fucked up thing about it. He knows he can't do anything. Do you want to know why he cant?'' I didn't let her get a word in edgewise. She needed to know the truth, no matter how bad that truth was. ``You are putting so much in the Church, when the damn church doesnt even believe you.'' I turned around. ``Isn't that right?'' He looked agast, but when he looked at the mother; all Father O'Hennessy saw was doubt. ``I believe that this is your cue to explain what I mean.''\\
He fingered the rosary around his neck, and chooned his lip. After a pregnant silence, he spoke up: ``You must understand. Real posessions are not as common as you might think.''
``You have got to be fucking with me!''\\
``Mrs. Loch please, The church cannot send their highly trained proffesionals to every supposed possession! And to be honest there hasn't been any proof yet!''\\
``No proof? No proof!'' She gafawed, and then her eyes shot right through the priest. She wanted to get this into his soul not just into the priest's ears. ``What about my son talking in a dead comma?''\\
``Mrs. Loch there are tons of evidence of that happening in normal commas.''\\
``The what about the shadows surrounding him in the security cameras?''\\
``The could be doctored in realtime. There could be any number of explanations. The church needs more proof in order to move forward with any sort of investigation.''\\
``Then what about the rat?'' I was done with this show.\\
The mother turned around and stared at me, ``You mean gunther? What about gunther?''\\
``Father O'Henessey, when Job was set against by the devil, was it not true that his stewardship, his flock, was tortured or even slaugthered?''\\
``Yes that is true, but what does that have to do with--''\\
``And Mrs. Loch, if I told you that Gunther was dead would you believe me?''\\
``Not in the slightest.''\\
``And why is that?'' Mrs loch stopped and looked at me. Then She started running to the kid's room. i followed and saw the familiar scene. The pale faced child no more then seven, hooked up to machines of all kinds. He was emaciated, and even though he was under a comma,  he looked like he is was in so much anguish. It took me a-back as I saw the child. This wasn't fair.\\
The mother took me out of my thoughts. ``See he is ok.'' She offered to let me hold him, and so I did. I pet the poor rat.\\
``There is just one problem.'' I looked her straight in the eyes, and with authority, ``Rats can't gag.'' The priest walked in and that was when it happened. The rat began to convulse and gag. I quickly put back the poor rat. ``Father, step out if you would.'' He listened supprisingly, and then as he left the room the rat went back to his normal self. ``I dont know, maybe its a coincidence that nature's lawas are being broken when ever there is the presence of the holy around this child?'' It wasnt really a qustion, but she took it as one.\\
``Do you think that the demon is affecting the rest of the house.''\\
``Yes and no. Demons are obssesed with life. They feed off of the life force of everything around it. Powerful demons that I have seen can sap the life out of towns. Hundreds of people at once, but this one is only able to affect a boy and his rat. But the demon is hardly able to affect the rat let alone the Jeremey.'' We started walking out of the room, and met with Father O'Hennessy. ``This is definitely a posession, fortunately for the boy, this isn't even a real demon. An imp most likely.''\\
``Are you sure about that? Peter Dane, full of pain, wont you make me whole again.'' It was a new voice. It was as deep as a tuba but as raspy sandpaper. There was the sounds of bones cracking and grinding. We looked up slowly all at once. There was the boy with blacked out eyes and skin some how more sallow before. The boy was crawling on Cieling above us and his head turned all the way around. The possed smiled as the mother screamed and the priest made the sign of the cross. ``Didn't You hear me? Peter Dane, full of Pain, won't you make me whole again.'' I opened my mouth to speak, but as soon as I did; The possesed boy open is mouth and started vomittinfg a black liquid as dark as any night. The possesed dropped from the cieling fell and fell right ontop of me, in a deeper and more crude voice unnatural to any child it screemed: ``PETERDANE! FULL OF PAIN! WON'T YOU MAKE ME WHOLE AGAIN!'' The Possesed begain clawing at my face, trying to scratch my eyes. Then it started headbutting me repeating the tripplet. Louder and Lauder it became until the sound was deafening. Then the barrage stopped.

\par The boy turned around aand looked at the priest. His arm was outstretched with a rosary presented. ``The power of christ compells you.'' The possesed boy stepped back mouthing no. ``I said that the Power of Christ compells you! The power of Christ compells you.'' With every time the priest said the words, the possesed reeled in agaony until he was back against the wall with me. I tried to say something but i couldnt my mouth was full of blood. I spit out what i could to yell but Father O'Hennessey wasn't listening, ``THE POWER OF CHRIST COMPELLS YOU!''\\
``Help me please!'' This time it sounded like the child's voice. Frantically I tried to speak but more blood and black liquid had filled my mouth.\\
``I will help you little lamb the power of Christ averts the demon.'' Then father O'Hennesey pointed now at the kid. ``I command you foul demon--'' The possesed jumped up and bit off the finger of the priest.\\
The thing started laughing uncontrollably. And it gyrated the boys hips. ``Didn't they tell you Peter Dane? Any child of the leviathans are great and powerful.'' I t was about to bight at my neck, But i wante the thing closer. I spit out the eucharist right into the child's face. Smoke and white fire began to billowing off of the childs face. But it was enough time for me clear my throat, and start praying what needed to be prayed. \\

\par ``Saint Michael the Achangel, defend us in battle. Be our protection against the wickedness and snares of the devil; May Adonai, The God of Holy Hosts, rebuke him, we humbly pray; O prince of the Holy Hosts, by the power of the Father, thrust into hell Satan and all evil spirits who seek the ruin of all holy men. And though I walk through valley of the shadow of death, I do not fear any evil, for you are with me lord. You are my rod and staff which I walk with. You are comfort and protect me. Cast out this wretch. Begone from the world of man, for the power of the Christ compells you!'' Then for good messure I pulled out a crucifix and placed it on the forehead of the child. There was a blood curddling scream.\\
``LEVIATHAN!'' Then like a sack of potatoes. The boy fell down out cold. I hadn't nticed it before but as soon as I cast the demon out the room went back to being lit by the sunlight. The worls was alittle more bright again.\\
\par I looked at the priest who was staring at me even though his finger was bitten off and was lying severed on the floor. ``You can't Just invoke the power of Christ just because you saw that in movies! Thers's nuance. And put that finger on Ice they might be able to save that.''\\

\chapter{}
\par While Father O'Henessey went to the hopital for a hunting accident I staid at the house observing the Boy and his rat. Both were perfectly healthy. Weak. But alive and healthy. The mother pulled me away at night. ``I thought you said that that\ldots thing wasnt powerful.''\\
``I never said that. What I said was that Powerful demon can affect whole towns. This one was hardly affecting anyoe else. This wasnt just any type of demon. It was a child of the Leviathan. Gluttony incarnate. There was a reason why it wasnt just sucking up as much life force as possible.''\\
``Why is that?'' She asked weakly.\\
``It was planning to suck your son dry. To wring your son of his entire soul and then it would have come for you.''\\
``So what it was a leech?''\\
``Exactly like a leech. However, how could it be brought into this world. There is no way that Jeremy knew how to invite a demon of that caliber into the world. These types of demons are special. They need to be invited into the world.'' I rubbed my chin but then cringed as the pain of the scratches reminded me of that night. ``The children of the Leviathan, make deals of gluttony. They are the ones that make vampires if you could believe it.''\\
``I didnt mean to call a demon.'' We turned around and there was young Jeremey. He was up and walking and looked more like he was tired rather than just possesed by a demon, but he pet his rat and cuddled the fat rat as if it was a teddy bear. ``Honest mister, I wanted help.''\\
``Well of course you didnt mean to call a demon. No one does. They are crafty and try to confuse you. Don't tell your mom I said this, but demons are assholes.'' I winked and that made him laugh.\\
But then he got somber all of a sudden. ``I wasn't tricked.'' I really wasn't I was reading from a prayer book.\\
``Sweety, I know but we dont have any prayer books.'' I cocked an eyebrow. She picked up on it and explained: ``We may say we are Catholic, But we are more like Easter Catholic. Especially after my Husband passed 3 months ago.'' I nodded as a matter of fact. Careful to make sure that she knew that I wasn't Judging her. I didnt go at all.\\
``Thats not true. I  have one.''\\
His mother was about to protest, but I cut her off: ``I would love to see this prayer book.'' I smiled softly. ``Please would you show me it.'' without missing a beat Jeremey turned around and starting limping back to is bed as he pet his rat. We followed. As we got into the room we saw that Jeremy was reaching under his bed and pulled something out.\\
He handed it over to me saying: ``The librarian said it would help. She said that this would help bring daddy back.'' The mother was about to burst with rage.\\
I interjected and said while looking at her, ``What a wonderful gesture.'' I took the book and smiled a bright smile. ``We will take a look at this and you will get to sleep. Put gunther back and make sure to give him some food he is a little low.'' Jeremey nodded, and then went back and started putting Gunther back into his cage. I took the mother's arm and left the room immediately. ``The last thing you need to do is get mad infront of him. He doesnt understand that this wasa set up.''\\
``I'm sorry.''\\
``I would be that mad too. Trust me.'' I chewed my lip, and then narrowed my eyes as I looked at the book. It was a leather bound book. \\
``What are those letters on that book.'' She asked, ``I have never seen any type of language like that.''\\
I breathed heavily looking at the words. ``Nor should you have. Its an ancient language. The first Language. It's Enochian: the language of Lucifer the Scribe.''\\
``A satanist Cursed my child!''\\
I smiled, ``No, not a satanist. Satanist's aren't who you think they are. Most believe that Satan was right: Humans were inherently evil and were a perversion to God's grace.'' She was obviousley confused, so I didnt spend time waiting for the inevitable question. ``The difference between what Judeo-Christians believe and what Satanists believe is that Judeo-Christians believe that we comitted original sin. That Adam and Eve took a bite from the Tree of Knowledge. That's why we sin. The core of the Satanic is that God made us imprerfect on purpose. Setting us up for failure. The point is\ldots this wasnt the work of a Satanist. Satanists use Latin and Aramaic.''\\
``Who uses Enocian then?''\\
``I am going to find out.''

\chapter{}

\par I looked at my watch. It was 3:00pm and school was getting out at any second. And as if on queue, the bell rang and kids streamed out like water. I walked on past all of them and quckly towards the library. Sure enough there was the librarian. She had black hair and couldn't have been more than fresh out of college. She swas putting books away on a ladder. She turned around and smiled. In a teasing tone she chuckled, ``Hey I dont care that it is after school I cant be oogled at openly.'' I didn't acknowledge the jab. I tossed the book ontop of the front desk. I fulled my arms across my chest. And with my eyes I gestured to the book.\\
``I care that you are about ten years younger than me. The book: That's some real heavy extracirricular studies. You know I swear they are teaching sex-ed and Enochian younger and younger.''\\
``Look its harmless it was just to take the kid's mind off of--''\\
``I dont have time for this.'' I took out my knife and cut my palm and quickly in enochian I said allowed, ``The shadow gluttony, the unholy Leviathan, here my call drain the room of all light. Make it perfect for the world. Make it prime for Lucifer the light-bringer!'' And almost instantaneously, the room went pitch black. It was a neat trick and it took far too long to learn it, but it told me alot.\\
``Oh my fucking god! Please dont hurt me!'' She kept rambeling and begging. Fortunately for her, this was only a spell to make darkness to increase the powers of occultists. But I was only using it to scare her. I let her unravel for a bit and then I repeated the prayer backwords wich brought the light back. When she could see again, she darted to me, ``What the fuck is your problem! No! What the fuck was that! No! Just\ldots Fuck!''\\
``No need to yell, you are still in a school.''\\
``You just Dumbeldored the entire room, how the fuck do you think I am not going to swear, and you have a knife what the hell! Why?''\\
I put away the knife, and started putting on bandages that I had prepared. I sighed. ``You didn't answer my answer my question. Quid pro quo.''\\
She slapped me, ``You are going to tell me who the fuck you are or I am going to call the cops.''\\
``Trust me,'' I said after feeling the reopened wound on my lip, ``You really do not want to get the cops involved, Jennifer.'' Before she could ask how I knew her name, I answerd that: ``I spoke to your dad. You know the Sheriff. Really nice guy, he bought me a coffee. I was hung over from dealing with the mess you made at the Loch household. You know before high and mighty, answer the question. The book.''\\
``Thats not a question old man.''\\
``First, I'm thirty-two. I'm not actually ten years older than you.'' That old man buisness hurt my ego a little, ``Second, either you are doing a great job of covering your ass over this fiasco because you know how much trouble you would be in,'' she started rubbing her arms chagrined, ``Or you had no idea what this thing was.'' I took out a cigarette and lit it up, she was going to stop me, but I stared her down and shook my head no. ``I am willing to give you the benifit of the doubt. But answer, and even make it easier for you, where did you get this, and more importantly why give it to a kid? For godsake.''\\

\par She closed the library early and took me to a bar. She wanted to make sure she was in a public place so that there was no way that I could try any more magic. I didn't mind. There was no way I would trust me after that. When we got our drinks she looked me dead in the eye and said, ``I really I had no idea that any of this shit was real.'' She took a deep drag of her beer and then asked for a cigarette. I obliged.``Listen, how could I had no idea that the kid would even read that thing. Fuck, I-- I was just trying to give him some peace you know? He was always so depressed and the school counseler was doing nothing about it. That's fucked up.''\\
``And your solution to a kid being a depressed about his father death, was to give him a book of spells that could open a doorway to demons if your not careful.'' Her face went pale, I rolled my eyes, ``I am careful. I know,'' I waved my hands around in the air, ``Generally what that book is.''\\
``Then why are you here if you already know what it is?''\\
``Generally.'' I took a healthy drink of my pint and then shook my head. ``I honestly thought you would know\ldots anything about it.''\\
``I didn't say that I didn't. I said I didn't know much. And you still haven't told me what happened.''\\
``Jeremy was possesed.'' She pat out her beer to the dismay of the bartender.\\
After the bartender cleaned up the mess, she asked in a hushed tone, ``Is he okay?''\\
``You didn't hear that he was in a coma for a week?''\\
``A coma? They told me that he was getting some psychiatric help. What the hell. Is he okay?''
``He is ok,'' I finished my beer and signaled for another, ``Well shaken up and sore from the contortions that he went through, but he will make it. He will definitely need psychiatric help now.'' She laughed an empty laugh, and she stared into her beer. She really didnt know what the thing was, or if she did she really wasn't a believer of what it stood for. ``Jennifer--''\\
``Jenny is fine.''\\
``Alright, Jenny\ldots I know you weren't trying to get the damn kid possesed. But I am going to need to know everything that you know.'' I put my hand on her shoulder. ``That's how you can make this better. By helping me make sure that this does not happen again.''\\
She nodded her hand and I took my hand of off her sholder. She looked and searched for something. Apparently she found it and said, ``As a way to combat my dad when I came back from college, I got into a group. They called themselves: dreamers, visionaries, and seers. Most of the people there are people in this small town, but the leader. He is the one that scares me a bit. He is intense. He leads these rituals and these prayer services to Satan. Not just Satan though. All other types of devils too. I didn't even know that there are other devils--''\\

\par ``Count yourself lucky'' I said after finishing my beer. ``There are 13 devils, each one was created by Lucifer as a mockery to God. Or so the Christians, and Jews think. Its more complicated than that. You see, Lucifer hated God's love for us. He knew we were imperfect, so with his free will he said as much to God. Lucifer told God that eventually humanity would reject him and even the paradise that he made. But God said that that was our free will just as he had his free will to bring the truth to him. But this angered Lucifer. Lucifer's truth was that God was perfect, why would God hurt humanity by making something that is imperfect. So to prove his point we get the story of Adam and Eve. Lucifer didn't just tempt Eve. He made it impossible to refuse. There was no tree of knowledge. It was the Tree of the Death. For humans could not die in the Garden of Eden, unless they ate of the Tree of Death. When Adam and Eve ate from that tree they didn't learn anything new. They realeased death into the Paradise.''\\
``Why would God put something like that in the Garden of Eden.''\\
``Do you know what the first book is?'' I said lighting my own cigarette. When she shook her head no, I bobbed mine. ``No, it's a book proscribed by the Church. It is the book of the bible that states what was God's plan for us if we did not eat from the tree of death, written by Lucifer himself.'' 


\end{document}

